Making decisions from samples with variable time costs

### 2014-12-19 jhamrick-cs281a.tex
Add results of statistical tests

% describe model from sources of uncertainty
As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}. Here, we assume this to be the case, and use the model from \citeA{Smith2012}. Briefly, their model incorporates four sources of uncertainty into the physical simulations: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$). To determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model. For each sample, we computed whether the ball went in the hole, and then averaged over all the samples.

@@

\subsection{Analysis}

\TODO{}

@@

On average, participants were correct about 76\% of the time ($\mu=0.76$, $\sigma^2=0.00001$), and responded that the ball would go in the hole about half the time ($\mu=0.53$, $\sigma^2=0.00001$). There was a significant effect of feedback type on participants' responses \TODO{}; there was also an effect of hole size, though less so \TODO{}. Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.

@@

Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms). There was a significant effect of feedback type on response time \TODO{}, however, there was not a large effect of hole size on response time, except in the case of the ``far in'' (FI) trials, in which the ball went straight through the center of the hole \TODO{}. Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.

>>>>

% describe model from sources of uncertainty
As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}. Here, we assume this to be the case, and use the model from \citeA{Smith2012}. Briefly, their model incorporates four sources of uncertainty into the physical simulations: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$). We fit these model parameters to human judgments in a related but separate task. Then, to determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model. From these samples, we estimated a truncated normal distribution along the wall with the hole in it, and then computed the probability density lying within the region of the hole.

@@

@@

On average, participants were correct 76.1\% of the time ($N=17686$) and responded that the ball would go in the hole 52.8\% of the time ($N=17686$). There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$). Additionally, there was an interaction between feedback type and hole size ($\chi^2(3)=64.469, p<0.001$). Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.

@@

Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms). There were significant effects of both feedback type ($\chi^2(3)=63.611, p<0.001$) and hole size ($\chi^2(1)=8.9808, p<0.01$) on response time, as well as an interaction between feedback type and hole size ($\chi^2(3)=27.146, p<0.001$). However, the hole size was only significant in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole. Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.
